\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}

\name{Terry G Lorber}
\address{\href{https://www.rideside.net/~tgl}{www.rideside.net/\texttildelow tgl} \\ \href{mailto:tgl@rideside.net}{tgl@rideside.net} \\ +1--781--632--0733}
                                        
\begin{document}
  
\begin{rSection}{Profile}
\item Consensus-building leader of cross-functional product development teams. I've developed strategy and implemented product roadmaps for startups to global businesses. Pro-active project manager experienced with quality systems for medical devices.
\end{rSection}

\begin{rSection}{Experience}

\begin{rSubsection}{Software Engineer, Architect}{June 2022 - November 2024}{\href{https://alloyenterprises.co}{Alloy Enterprises}}{Burlington, MA}
\item Planned, built, and maintained proprietary CAD/CAM software to support Alloy's novel manufacturing process. Collaborated across disciplines to unlock aluminum components at scale.
\item Software Engineering, Computational Geometry, Manufacturing, Python, C++
\end{rSubsection}

\begin{rSubsection}{Consultant}{December 2018 - June 2022}{\href{https://metatooth.com/services}{Self-employed}}{Swampscott, MA}
\item Consulting services in advanced manufacturing, technology integration, and product development.
\end{rSubsection}

\begin{rSubsection}{VP of Software}{August 2017 - December 2018}{\href{https://lightforceortho.com}{LightForce Orthodontics}}{Cambridge, MA}
\item Joined this pre-seed round dental startup as first software hire. Responsible for medical device and workflow software in support of company's first sale. Deployed cloud-native software stack for LightForce's first 510(K). Contributed system architecture, implementation, regulatory documentation, project management, and product management.
\item Medical Devices, FDA, JavaScript, C++, Computational Geometry
\item \textbf{510(K) No. K183542} Signature Orthodontics System, 2019-01-02
\item \textbf{510(K) No. K181271} Signature Orthodontics System, 2018-06-13
\end{rSubsection}


\begin{rSubsection}{Director, Global Digital Product Development}{August 2010 - August 2017}{\href{https://dentsplysirona.com}{Atlantis - Dentsply Sirona}}{Waltham, MA}
\item Responsible for digital dentistry strategy and project planning for global business. Leader of cross-functional product development team that launched Atlantis' first digital product. Collaborated with business partners to deliver integrated digital workflows.
\item Product Development, Cross-functional Team Leadership, Medical Devices, Manufacturing, Business Development
\item \textbf{US Patent No. 10,390,910 B2} INTEGRATED DENTAL IMPLANT COMPONENT AND TOOL FOR PLACEMENT OF A DENTAL IMPLANT COMPONENT
\item \textbf{US Patent No. D787,061S} SCAN BODY FOR DENTAL IMPLANT PROCEDURES
\end{rSubsection}

\begin{rSubsection}{Consulting Software Engineer}{January 2007 - July 2010}{\href{https://dentsplysirona.com}{Atlantis - Astra Tech}}{Waltham, MA}
\item Technical owner of industry leading B2B platform. Full stack development using JavaScript, Ruby on Rails, PostgreSQL, and C++. Collaborated with business partners to deliver integrated digital dentistry workflows.
\item Software Engineering, Medical Devices, Manufacturing, Ruby on Rails, C++, Computational Geometry
\end{rSubsection}

\begin{rSubsection}{Senior Software Engineer}{August 2000 - January 2007}{\href{https://dentsplysirona.com}{Atlantis Components}}{Cambridge, MA}
\item First software hire for this dental startup. Supported sales \& manufacture of industry's first CAD/CAM dental implant abutment. Automation of data acquisition, product design, and manufacturing workflows
\item Software Engineering, Medical Devices, Manufacturing, C++, Ruby on Rails
\end{rSubsection}

\begin{rSubsection}{Product Engineer}{June 1996 - September 1999}{\href{https://fst.com}{Freudenberg Sealing Technologies}}{Bristol, NH}
\item Product design, prototyping, and testing in support of sales and manufacturing. My first experience with Kaizen and continuous improvement culture.
\item C, Siemens NX, Computer-Aided Design (CAD), Manufacturing
\end{rSubsection}

\end{rSection}

\begin{rSection}{Education}

\item {\bf Boston University, Boston, MA} \hfill {\em September 2013} \\
M.S. in Computer Science

\item {\bf University of Michigan, Ann Arbor, MI} \hfill {\em May 1996} \\
B.S. in Engineering (Mechanical Engineering)

\end{rSection}


\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Bash, C++, JavaScript, Python, R, Ruby, SQL, TypeScript \\
Operating Systems & Browsers (Chrome, Firefox), Linux (Ubuntu), macOS, Windows \\
Protocols \& APIs & HTTPS, JSON, REST, RPC, WSS, XML, YAML \\
Databases & MS SQL Server, PostgreSQL, Redis, Sqlite3 \\
Web \& App servers & flask, NGINX, node.js, puma \\
Tools & AWS, Azure, CMake, Docker, Emacs, GitHub, Jira, WordPress \\
Frameworks & CGAL, FLTK, Node.js, OpenGL, OpenMesh, Ruby on Rails, \\
 & Sinatra.rb, three.js, Unidraw, VTK, Vue.js \\
Methodologies & Agile, Continuous Improvement, Kaizen, KanBan \\
Infleuncers & Atwood's Coding Horror, Beck's XP, Booch's UML, \\
 & Brooks' The Mythical Man-Month, DeMarco \& Lister's Peopleware, \\
 & Fowler's Continuous Integration, Spolsky's Joel on Software, \\
 & Gamma, Helm, Johnson, and Vlissides's Design Patterns, \\
 & Tufte's Visual Display of Quantitative Information
\end{tabular}
\end{rSection}

\begin{rSection}{Extra}
\item Programmer, Gardener, Brewer, Hiker, Surfer, Telemark skier
\item Town Meeting Member | Swampscott, MA | 2018-2024
\item Cubmaster Pack 55 | Swampscott, MA | 2018-2021
\item UM College of Engineering Leadership Honor Society | Ann Arbor, MI | 1995-1996
\item Eagle Scout Troop 295 | Concord, NH | 1991
\end{rSection}

\end{document}
