\documentclass{resume}
\usepackage{fontspec}
\setmainfont{TeX Gyre Termes}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\hypersetup{pdftitle={Terry G Lorber II}}

\name{Terry G Lorber II}
\address{Swampscott, MA \\ \href{mailto:tgl@rideside.net}{tgl@rideside.net} \\ +1--781--632--0733}
                                        
\begin{document}

\begin{rSection}{Profile}
\item Consensus-building leader of cross-functional product development teams. I've developed strategy and implemented product roadmaps for startups to \$100M global businesses. Pro-active project manager experienced with quality systems for medical devices.
\end{rSection}

\begin{rSection}{Experience}

\begin{rSubsection}{Founding Software Engineer}{March 2025 - June 2026}{\href{https://fabublox.com}{FabuBlox}}{Boston, MA}
\item Process design, simulation, and visualization software for semiconductor device manufacture.
\item Software Engineering, Computational Geometry, C++, TypeScript    
\end{rSubsection}
    
\begin{rSubsection}{Software Engineer, Architect}{June 2022 - November 2024}{\href{https://alloyenterprises.co}{Alloy Enterprises}}{Burlington, MA}
\item Product design, analysis, and workflow software to support Alloy's novel manufacturing process.
\item Software Engineering, Computational Geometry, Manufacturing, Python, C++
\end{rSubsection}

\begin{rSubsection}{Consultant}{December 2018 - June 2022}{\href{https://metatooth.com/services}{Self-employed}}{Swampscott, MA}
\item Advised businesses on advanced manufacturing, technology integration, and product development.
\end{rSubsection}

\begin{rSubsection}{Founding Software Engineer}{August 2017 - December 2018}{\href{https://lightforceortho.com}{LightForce Orthodontics}}{Cambridge, MA}
\item Joined this pre-seed round dental startup as first software hire. Responsible for medical device and workflow software in support of company's first product sale. Contributed system architecture, implementation, regulatory documentation, project management, and product management.
\item Medical Devices, FDA, JavaScript, C++, Computational Geometry
\item \textbf{510(K) No. K183542} Signature Orthodontics System, 2019-01-02
\item \textbf{510(K) No. K181271} Signature Orthodontics System, 2018-06-13
\end{rSubsection}

\begin{rSubsection}{Director, Global Digital Product Development}{August 2010 - August 2017}{\href{https://dentsplysirona.com}{Dentsply Sirona - Atlantis}}{Waltham, MA}
\item Strategy and project planning for global digital business. Led technical product and project management with team of five engineers.
\item Product Development, Cross-functional Team Leadership, Medical Devices, Manufacturing
\item \textbf{US Patent No. 10,390,910 B2} INTEGRATED DENTAL IMPLANT COMPONENT AND TOOL FOR PLACEMENT OF A DENTAL IMPLANT COMPONENT
\item \textbf{US Patent No. D787,061S} SCAN BODY FOR DENTAL IMPLANT PROCEDURES
\end{rSubsection}

\begin{rSubsection}{Principal Software Engineer}{January 2007 - July 2010}{\href{https://dentsplysirona.com}{Astra Tech - Atlantis}}{Waltham, MA}
\item Technical owner of industry leading B2B platform.
\item Software Engineering, Medical Devices, Manufacturing, Ruby on Rails
\end{rSubsection}

\begin{rSubsection}{Founding Software Engineer}{August 2000 - January 2007}{\href{https://dentsplysirona.com}{Atlantis Components}}{Cambridge, MA}
\item First software hire for this dental startup. Automation of data acquisition, product design, and manufacturing workflows.
\item Software Engineering, Medical Devices, Manufacturing, C++, Computational Geometry
\end{rSubsection}

\begin{rSubsection}{Product Engineer}{June 1996 - September 1999}{\href{https://fst.com}{Freudenberg Sealing Technologies}}{Bristol, NH}
\item Product design, prototyping, and testing in support of sales and manufacturing. My seminal experience with Kaizen and continuous improvement culture.
\item C, Siemens NX, Computer-Aided Design (CAD), Manufacturing
\end{rSubsection}

\end{rSection}

\begin{rSection}{Education}

  \begin{rSubsection}{M.S. in Computer Science}{June 2010 - September 2013}{\href{https://www.bu.edu/}{Boston University}}{Boston, MA}
  \item[]
  \end{rSubsection}

  \begin{rSubsection}{B.S. in Engineering (Mechanical Engineering)}{September 1992 - May 1996}{\href{https://www.umich.edu/}{University of Michigan}}{Ann Arbor, MI}
  \item[]
  \end{rSubsection}

\end{rSection}


\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Bash, C++, C\#, JavaScript, Python, R, Ruby, SQL, TypeScript \\
Operating Systems & Browsers (Chrome, Firefox), Linux (Ubuntu), macOS, Windows \\
Protocols \& APIs & HTTPS, JSON, REST, RPC, WSS, XML, YAML \\
Databases & MariaDB, MongoDB, PostgreSQL, Redis, Sqlite3 \\
Web \& App servers & express.js, flask, NGINX, puma \\
Tools & AWS, Azure, Claude Code, Codex, CMake, Conan, Docker, Emacs, \\
 & Gemini, Git, GitHub Actions, GitHub Copilot, Google Cloud Platform, \\
 & Google Docs \& Sheets, Jira, Linear.app, tmux, WordPress \\
Libraries & CGAL, Clipper2, Eigen, FLTK, GEOS, .NET, Node, \\
 & OpenGL, OpenMesh, React, Ruby on Rails, Sinatra.rb, three.js, \\
 & Unidraw, VTK, Vue.js \\
Methodologies & Agile, Continuous Improvement, Kaizen, KanBan \\
Infleuncers & Atwood's Coding Horror, Beck's XP, Booch's UML, \\
 & Brooks' The Mythical Man-Month, DeMarco \& Lister's Peopleware, \\
 & Fowler's Continuous Integration, Spolsky's Joel on Software, \\
 & Gamma, Helm, Johnson, and Vlissides's Design Patterns, \\
 & Tufte's Visual Display of Quantitative Information
\end{tabular}
\end{rSection}

\begin{rSection}{Extra}
\item \href{https://48bottles.com}{Brewer}, \href{https://www.tiktok.com/@growherbert}{Gardener}, Hiker, \href{https://github.com/terryg}{Programmer}, Telemark skier
\item Town Meeting Member | Swampscott, MA | 2018-2026
\item UM College of Engineering Leadership Honor Society | Ann Arbor, MI | 1995
\item Eagle Scout Troop 295 | Concord, NH | 1991
\end{rSection}

\end{document}
